The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 Finally, the comparison between \Cref{fig__jetI5+ismSeed3-45deg-CR} and\
 \Cref{fig__jetI5+ismSeed3-45deg} shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
 We thefore stress that\
 assuming $p_{CR}\ll p_{\text{gas}}$ in \Cref{governing-eq} is resonable.

>>>>

 Finally, the comparison between\
 \Cref{fig__jetI5+ismSeed3-45deg}\
 and\
 \Cref{fig__jetI5+ismSeed3-45deg-CR}\
 shows that the CR pressure\
 is around 5$\times10^{-15}$--8$\times10^{-15}$ erg/cm$^{3}$, less than the gas pressure by a factor 10--20.\
 We thefore stress that\
 ignoring the contribution of CR pressure gradient to the momentum of the gas\
 in \Cref{governing-eq} is resonable.
